%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{natbib}
\usepackage{bibentry}
\newcommand{\bibverse}[1]{\begin{verse}\bibentry{#1}. \end{verse}}
\name{Maryam Babaee} % Your name
\address{Wittelsbacherstr. 18-82110 Germering} % Your secondary addess (optional)
\address{(0176)--86261666 \\ mar.babaee@gmail.com} % Your phone number and email
%\address{Institute for Human-Machine Communication \\ Technische Universit\"at M\"unchen (TUM)} % Your address


\nobibliography*
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

%{\bf PhD student in Electrical Engineering at TUM, Germany} \hfill {2012--present} \\ 
%Advisor: \textbf{Prof. Gerhard Rigoll.} Co-advisor:\textbf{Prof Mihai Datcu}\\
%Thesis topic:''Immersive Visual Data Mining; Application to Radar Images''\\
%\linebreak
{\bf M.Sc. in Artificial Intelligence, University of Isfahan, Iran} \hfill {Oct. 2012 -- Jul. 2014} \\ 
Thesis title: ''3-D Reconstruction of Vessels from Two Uncalibrated Mammography Images''\\
\linebreak
{\bf B.Sc. in Computer Engineering, University of Tehran, Iran} \hfill {Oct. 2006 -- Jul. 2011} \\ 
Thesis title: ''Designing DBRG (Database Research Group) Website in Content Management System (WordPress)''

%{ High school diploma in Math/Physics at Salamatian high school, Isfahan, Iran} \hfill {1994--1998} \\ 
\end{rSection}


\begin{rSection}{Awards and Honors}
	\begin{itemize}
		\item{Ranked as 1099th in National Universities Entrance Exam among about 400,000 Students.}\vspace{-0.2cm}
	\end{itemize}
\end{rSection}

\begin{rSection}{Practical Experiences}

\begin{itemize}
\item{
\begin{rSubsection}	{Evolutionary Algorithms}{09.2012-11.2012 (20 h/w)}{Univ. of Isfahan}{}
	\begin{itemize}
 \item {Combining fuzzy logic and genetic algorithms for classifying IRIS data} 
\end{itemize}
\end{rSubsection}}

\item{
\begin{rSubsection}{Pattern Recognition}{05.2012-07.2012 (25 h/w)}{Univ. of Isfahan}{}
	\begin{itemize} 
		\item {Recognition of Farsi Bank Bills. In this project, which was completed in Matlab, PCA and LDA techniques were used to reduce the dimensionality of feature space. At the end, K-nearest neighbor as a classifier was used to recognize different amount of bills.} 
		\end{itemize}
\end{rSubsection}}

\item{
\begin{rSubsection}{Digital Signal Processing}{06.2012-07.2012 (12 h/w)}{Univ. of Isfahan}{}
	\begin{itemize}
		\item {Voice imitation and equalization by changing the frequency components using the Voice Processing toolbox in Matlab } 
		\end{itemize}
\end{rSubsection}}

\item{
\begin{rSubsection}{General Workshop}{09.2011-10.2011 (20 h/w)}{Univ. of Tehran}{}
	\begin{itemize}
		\item {Programming an AVR micro controller for a line follower robot using. In this project, the program of the robot was implemented in C in order to control the robot to follow a predefined line.}\vspace{-0.2cm}
		\end{itemize}
\end{rSubsection}}

\item{
\begin{rSubsection}{Internet Engineering}{04.2009-05.2009 (20 h/w)}{Univ. of Tehran}{}
	\begin{itemize}
		\item{Design and implementation of a web application for pizza delivery system using Hibernate framework, Apache Tomcat server, Java, HTML, and Javascript}
	\end{itemize}
\end{rSubsection}}

\item{
\begin{rSubsection}{Computer Network}{10.2008-11.2008 (30 h/w)}{Univ. of Tehran}{}
	\begin{itemize}
		\item{Implementation of a chat server with the ability of sending and receiving files in Linux operating system using C}
	\end{itemize}
\end{rSubsection}}


\item{
\begin{rSubsection}{Operating System}{10.2008-12.2008 (15 h/w)}{Univ. of Tehran}{}
	\begin{itemize}
		\item{Implementation of a synchronizer application over network in Linux operating system using multi threading methods using C language}
	\end{itemize}
\end{rSubsection}}


%\begin{rSubsection}{Course Project}{Fall 2007}{Computer Architecture}{University of Tehran, Iran}
	%\begin{itemize}
		%\item{Design and implementation of roll-call system in an organization}\vspace{-0.2cm}
    %\end{itemize}
%\end{rSubsection}

\item{
\begin{rSubsection}{Assembly and Machine Language}{10.2007-12.2007 (20 h/w)}{Univ. of Tehran}{}
	\begin{itemize}
		\item{Implementation of a two player game application in assembly language.}
    \end{itemize}
\end{rSubsection}

\item{
\begin{rSubsection}{C++ Programming}{04.2007-05.2007 (20 h/w)}{Univ. of Tehran}{}
	\begin{itemize}
		\item{Object Oriented Programming in C++. In this project, a game application was reimplemented by replacing the architecture of the application with several classes.}
    \end{itemize}
\end{rSubsection}}
\end{itemize}
\end{rSection}

\vspace{.5cm}
\begin{rSection}{Research Experience}
\begin{rSubsection}{Research assistance at MMK (Mensch-Maschine-Kommunikation), TU Munich, Germany}{}{}{}
	\begin{itemize}
		\item {Multiple target tracking in a multi-view crowded environments}\vspace{-0.2cm}
		\item{Non-negative matrix factorization for dimensionality reduction}\vspace{-0.2cm}	
	\end{itemize}
\end{rSubsection}
\vspace{.3cm}
\begin{rSubsection}{Artifical Intelligence Group- University of Isfahan}{}{}{}
	\vspace{.2cm}
	\begin{itemize}
		\item {3-D Reconstruction of Vessels from Two 2-D Uncalibrated Mammography Images }\vspace{-0.2cm}
		\item {Recognition of Farsi bank bills using PCA and LDA }\vspace{-0.2cm}
		\item {Combining fuzzy logic and genetic algorithms for classifying IRIS data }\vspace{-0.2cm}
	\end{itemize}
\end{rSubsection}
\end{rSection}



\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & C/C++, Java, Visual Basic, Lisp, Assembly (80x86) \\
Programming Packages & MATLAB, OpenCV, OpenGL, \\
Tools & Latex, Visual Studio, Quartus and Modelsim, 3D Max, MeshLab \\
Web Development &HTML, Javascript, CSS\\
\end{tabular}
\end{rSection}

%\begin{rSection}{Selected Graduate Courses}
	%\begin{itemize}
		%\item{Computer Vision}\vspace{-0.3cm}
		%\item{Pattern Recognition}\vspace{-0.3cm}
	%\item{Digital Image Processing}\vspace{-0.3cm}
	%\item{Neural Network}\vspace{-0.2cm}		
	%\item{Digital Signal Processing}\vspace{-0.2cm}		
	%\end{itemize}
%\end{rSection}

\begin{rSection}{Spoken Languages}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
English & Fluent in written and spoken \\
Persian & Native\\
German & Basic
\end{tabular}
\end{rSection}

\begin{rSection}{Interests}
Traveling, Reading, Chess, Movies, Computer Programming
\end{rSection}


%\begin{rSection}{Publications}
%\begin{rSubsection}{Technical Reports}{}{}{}
%\vspace{2mm}
%\begin{itemize}
%\item \bibentry{mymasterThesis2014}.
%\end{itemize}
%\end{rSubsection}
%%\begin{rSubsection}{Journal Papers}{}{}{}
%%%\cite{*}
%%\vspace{2mm}
%%\begin{itemize}
%%\item \bibentry{babaee2014optiacousticcviu}.
%%\end{itemize}%
%%%\renewcommand{\section}[2]{}
%%%
%%%\bibliography{Mypubs}
%%\end{rSubsection}
%\begin{rSubsection}{Refereed Conference Papers}{}{}{}
%%\cite{*}
%\vspace{2mm}
%\begin{itemize}
%\item \bibentry{babaee2014mammography}.
%
%%\renewcommand{\section}[2]{}
%\end{itemize}%
%%%
%%%\bibliography{Mypubs}
%\end{rSubsection}
%
%\begin{rSubsection}{Posters}{}{}{}
%%\cite{*}
%\vspace{2mm}
%\begin{itemize}
%\item \bibentry{synthetic2014}.
%%\item \bibentry{terasar2013dlr}.
%%\item \bibentry{bigdata2012esa}.
%%\item \bibentry{iim2012dlr}.
%\end{itemize}%
%%%\renewcommand{\section}[2]{}
%%%
%%%\bibliography{Mypubs}
%\end{rSubsection}




%\end{rSection}


%% generated by http://www.monperrus.net/martin/bibtex2latex
%% encoding: UTF-8 


%\bibliographystyle{plain}
%\nobibliography{Mypubs}
















%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------


%------------------------------------------------


%------------------------------------------------




%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}




